ext_risk_copula

### 2019-01-25 ext_risk_copula.Rmd
try to add malthus model

rlist<-c(0,0.1,0.3,0.5,0.7,0.9,1.0,1.1,1.3,1.5,1.7,1.9) #rc = 1
numsims<-10000
numsteps<-25
numlocs<-5
a<-NA
b<-NA
K<-50
scl<-1
ext_thrs<-K/10
model<-"ricker"

@@

# plot for local dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
pdf(paste(resloc,"ricker_ext_risk_local_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(i in c(1:length(rlist))){
    r<- rlist[i]
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,ploton = F)
    ricker_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    ricker_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

@@

# plot for local dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
pdf(paste(resloc,"ricker_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    #cat("r=",r,"\n")
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

@@

# plot for local dispersal in D matrix 
pdf(paste(resloc,"hassell_ext_risk_local_disp.pdf",sep=""),height=9,width=15)
op<-par(mfrow=c(3,5),mar=c(5.2,4.2,1.2,1.2))
for(i in c(1:length(rlist))){
    r<- rlist[i]
    K_e<-((r^(1/b))-1)/a
    K<-K_e
    ext_thrs<-K/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,ploton = F)
    hassell_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    hassell_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

@@

# plot for local dispersal in D matrix 
pdf(paste(resloc,"hassell_ext_risk_global_disp.pdf",sep=""),height=9,width=15)
op<-par(mfrow=c(3,5),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    #cat("r=",r,"\n")
    K_e<-((r^(1/b))-1)/a
    K<-K_e
    ext_thrs<-K/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

@@

# plot for local dispersal in D matrix 
pdf(paste(resloc,"msmith_ext_risk_local_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(i in c(1:length(rlist))){
    r<-rlist[i]
    K_e<-((r-1)^(1/b))/a
    K<-K_e
    ext_thrs<-K/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,ploton = F)
    msmith_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    msmith_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

@@

# plot for global dispersal in D matrix 
pdf(paste(resloc,"msmith_ext_risk_global_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    K_e<-((r-1)^(1/b))/a
    K<-K_e
    ext_thrs<-K/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

@@

# plot for local dispersal in D matrix 
pdf(paste(resloc,"pennycuick_ext_risk_local_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(i in c(1:length(rlist))){
    r<-rlist[i]
    K_e<-(b/a)*(a+log(r-1))
    K<-K_e
    ext_thrs<-K/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,ploton = F)
    pennycuick_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    pennycuick_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

@@

# plot for global dispersal in D matrix 
pdf(paste(resloc,"pennycuick_ext_risk_global_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    K_e<-(b/a)*(a+log(r-1))
    K<-K_e
    ext_thrs<-K/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

>>>>

rlist<-c(0,0.1,0.3,0.5,0.7,0.9,1.0,1.1,1.3,1.5,1.7,1.9) #rc = 1
numsims<-10000
numsteps<-25
numlocs<-5
K<-50
scl<-1
ext_thrs<-K/10
model<-"ricker"

@@

# plot for local dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
pdf(paste(resloc,"ricker_ext_risk_local_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,K)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,ploton = F)
    ricker_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    ricker_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

@@

# plot for local dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
pdf(paste(resloc,"ricker_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,K)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

@@

# plot for local dispersal in D matrix 
pdf(paste(resloc,"hassell_ext_risk_local_disp.pdf",sep=""),height=9,width=15)
op<-par(mfrow=c(3,5),mar=c(5.2,4.2,1.2,1.2))
for(i in c(1:length(rlist))){
    r<- rlist[i]
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,ploton = F)
    hassell_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    hassell_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

@@

# plot for local dispersal in D matrix 
pdf(paste(resloc,"hassell_ext_risk_global_disp.pdf",sep=""),height=9,width=15)
op<-par(mfrow=c(3,5),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    #cat("r=",r,"\n")
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

@@

# plot for local dispersal in D matrix 
pdf(paste(resloc,"msmith_ext_risk_local_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(i in c(1:length(rlist))){
    r<-rlist[i]
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,ploton = F)
    msmith_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    msmith_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

@@

# plot for global dispersal in D matrix 
pdf(paste(resloc,"msmith_ext_risk_global_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

@@

# plot for local dispersal in D matrix 
pdf(paste(resloc,"pennycuick_ext_risk_local_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(i in c(1:length(rlist))){
    r<-rlist[i]
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,ploton = F)
    pennycuick_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    pennycuick_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

@@

# plot for global dispersal in D matrix 
pdf(paste(resloc,"pennycuick_ext_risk_global_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```
